\subsection{Time Resource (TCR)} 

The resource architecture is the implemented using the Observer Pattern.

TCR is the \textbf{Observable} process. At regular time intervals each
\textbf{Observer} time affected entity is notified about current time.

Once registered by TCR, TAE immediately starts being fed with periodic time
passing messages.

To allow variable time simulation speed, TCR implements a method to increment
the speed of time increase. For simplicity and to stimulate implementation of
statistic event triggering, absolute time distance between calls to
notifyObservers() calls will always be fixed, and regulated by some internal
thread. The time passed will increase more or less depending on current sim
speed.

Simulation speed must also be changeable dynamically.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection{Simulation Resource (SCR)} 

Holds a status and a set of simulated resources(SR). Is a time affetected
resource.

Access to simulated resources is done with the following interface

\begin{verbatim}
public interface SimulatedResourceAccess {
	
	Object request(String: resource_name, Object request); 

}
\end{verbatim}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\subsection{Simulated Resource (SR)} 

Is represented by the following interface:

\begin{verbatim}
public interface SimulatedResource {
	
	Double getAmount();

}
\end{verbatim}

Currently there are two simulated resources:

\begin{enumerate}
  \item Fuel (FUC)
  \item Food (FOC)
\end{enumerate}
